Geospatial - Assignment 1

### 2025-01-27 hw1/submission_notebook.Rmd
Knitted HTML document

---
title: "Geospatial - Assignment 1 - Moritz Peist, Noemi Lucchi, Simon Vellin"
output:
  html_document:
    toc: true
  pdf_document:
    toc: true
---

@@

In the following notebook we replicate the charts for all 5 papers. Contentwise, the code follows always the same structure. We first load the data, then we create the chart and finally we save the chart as a .png file.

@@

# RSA boundaries - downloaded from GDAM and temporarily stored
sa_districts_sf <- st_as_sf(gadm(country = "ZAF", level = 3))

@@

In comparison the third paper map looked as follows: ![Figure 4](data/paper3/original_plot.png)

@@

In comparison the fourth paper map looked as follows: ![Figure x]()

@@

In comparison the fifth paper map looked as follows: ![Figure x]()

>>>>

---
title: "Geospatial - Assignment 1"
author: 
- Moritz Peist
- Noemi Lucchi
- Simon Vellin
output:
  html_document:
    toc: true
  pdf_document:
    toc: true
---

@@

In the following notebook we replicate the charts for all 5 papers. Contentwise, the code follows always the same structure. We first load the data, then we create the chart and finally display it.

@@

# RSA boundaries - downloaded from GDAM
sa_districts_sf <- st_as_sf(gadm(country = "ZAF", level = 3))

@@

In comparison the third paper map looked as follows:

![Figure 4](data/paper3/original_plot.png)

@@

In comparison the fourth paper map looked as follows:

![Figure x]()

@@

In comparison the fifth paper map looked as follows:

![Figure x]()
